Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-13 documents/TriangleScenarioArXiv/ts.tex
Fixed up conclusion, removed refinement 3

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

    Ultimately, this work accomplishes two important tasks. First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems. The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at. In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure. Consequently, this work strongly indicates that the Inflation Technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory. Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations. In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.

    In consideration of our resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{1}
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
    \end{enumerate}

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle structure (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

    Ultimately, this work accomplishes two important tasks. First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems. The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at. In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure. Consequently, this work strongly indicates that the Inflation Technique has the potential to solve an assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory. Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations. In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} In consideration of our resolution to \ref{r:1}, we propose an alternative reinterpretation of Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:

    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{1}
        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
    \end{enumerate}

    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.

    Using the Inflation technique, it became possible to provide a stronger proof of non-classicality than proposed by Fritz~\cite{Fritz_2012}. In particular, noisy variants of the Fritz distribution are provably non-classical (\cref{sec:noise}) and there exist quantum distributions quantitatively distinct from the Fritz distribution which admit greater numerical violations (\cref{sec:optimizations}). Despite these advancements, the distributions obtained closely resemble the Fritz distribution indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure. Currently, it remains speculative about how to recognize whether or not a given distribution for the Triangle structure exhibits non-classical correlations that maintain distinct qualitatively advantages from a resource perspective. One possibility is to extend \cref{r:2} to include the necessity of entanglement measurements. Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.
